Computing Direct Sum Decompositions

### 2024-12-31 paper/main.tex
uncommitted changes

%% \author{Devlin Mallory}
%% \affiliation{Basque Center for Applied Mathematics, Bilbao, Basque Country, Spain}
%% \email{\href{mailto:dmallory@bcamath.org}{dmallory@bcamath.org}}

%% \author{Mahrud Sayrafi}
%% \affiliation{Max Planck Institute for Mathematics in the Sciences, Leipzig, Germany}
%% \email{\href{mailto:mahrud@mis.mpg.de}{mahrud@mis.mpg.de}}

@@

After describing the algorithm and proving its correctness, we present multiple examples, including some which present previously unknown phenomena regarding the behavior of summands of Frobenius pushforwards and syzygies over Artinian rings. In particular, we highlight the results of \cite{CDE+24}, which shows a recurrence formula for indecomposable summands of high syzygies of the residue field of Golod rings, made possible through experiments and observations using our algorithm.

@@

\begin{exa}[Syzygies over Artinian rings]
  % https://arxiv.org/abs/2208.05427
  In recent work suggested by examples calculated using our algorithm, \cite{CDE+24} studies the indecomposable summands of syzygy modules over a Golod ring $(R,m,k)$. In particular, they find previously unexpected recurring behavior, specifically that the syzygy modules of the residue field are direct sums of only three indecomposable modules: the residue field $k$, the maximal ideal $m$, and an additional module $N = \Hom_R(m, R)$.

>>>>

%% \author{Devlin Mallory}
%% \address{Basque Center for Applied Mathematics, Bilbao, Basque Country, Spain}
%% \email{\href{mailto:dmallory@bcamath.org}{dmallory@bcamath.org}}

%% \author{Mahrud Sayrafi}
%% \address{Max Planck Institute for Mathematics in the Sciences, Leipzig, Germany}
%% \email{\href{mailto:mahrud@mis.mpg.de}{mahrud@mis.mpg.de}}

@@

After describing the algorithm and proving its correctness, we present multiple examples, including some which present previously unknown phenomena regarding the behavior of summands of Frobenius pushforwards and syzygies over Artinian rings. In particular, we highlight the results of \cite{CDE24}, which shows a recurrence formula for indecomposable summands of high syzygies of the residue field of Golod rings, made possible through experiments and observations using our algorithm.

@@

\begin{exa}[Syzygies over Artinian rings]
  % https://arxiv.org/abs/2208.05427
  In recent work suggested by examples calculated using our algorithm, \cite{CDE24} studies the indecomposable summands of syzygy modules over a Golod ring $(R,m,k)$. In particular, they find previously unexpected recurring behavior, specifically that the syzygy modules of the residue field are direct sums of only three indecomposable modules: the residue field $k$, the maximal ideal $m$, and an additional module $N = \Hom_R(m, R)$.
